% Cover letter using letter.cls
\documentclass[10pt]{letter} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8.5in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
\newcommand*\wrapletters[1]{\wr@pletters#1\@nil}
\def\wr@pletters#1#2\@nil{#1\allowbreak\if&#2&\else\wr@pletters#2\@nil\fi}
\begin{document}


\signature{Xi He}                  % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{Mr. Jamie Miller, Mindex Technology Inc.  \\
3495 Winton Place Plaza \\
Building E, Suite 4  \\
Rochester, NY 14623 } 

\begin{center}
\large\bf Xi He\\
118 East Squire Drive \#8\\ Rochester, NY 14623 \\ (404) 518-3581
\end{center} 
\vfill % forces letterhead to top of page


 
\opening{Dear Mr. Jamie Miller,} 
 
\noindent I am writing to inquire about the career opportunity as a Java software engineer.
I am very interested in working as a Java server developer or a Java Web Services developer at Mindex Technologies Inc. 
 
\noindent I will be graduating from Rochester Institute of Technology in May with a Master of Science degree in Computer Science. As shown in my resume, I have strong Computer Science background, holding a Computer Science Bachelor degree and a Computer Science Master degree and working as a software engineer for 3 years in China. While working as a Java software engineer, my colleagues and I spent 2 years developing a new Banking System for China MinSheng Bank.  I also worked as a lecturer in the Web Services class when I pursued my Master degree in China. Being a Java enthusiast, I like to study open source software like Structs or Axis in my spare time and am also a Sun Certified Programmer. 

At RIT, I have developed a very unique educational experience that has combined the practical aspects of a career education with the creativity of a research education. I have also become proficient in applying the Computer Science theory I have learned in the classroom to the actual project. Currently, I am working with my advisor Professor Kaminsky on Parallel Java, a API and middleware for parallel programming in Java. Our goal is to develop a Java based efficient platform for parallel computing. As a result of these experiences, I am confident that I will bring both technical skills and a fresh perspective to Mindex Technologies Inc.
 
\noindent I am enclosing my resume. My personal information can also be viewed online at \wrapletters{http://sites.google.com/site/hexi111/home}.
I would appreciate an interview with you at your convenience. 

I look forward to talking with you soon. Thank you for your consideration.
 
\closing{Sincerely yours,}
 
 
\encl{}  				% Enclosures

\end{letter}
 

\end{document}




