% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document} 
 
\name{~~~~Xi He\\xi.he@mail.rit.edu\\~~(404) 518-3581\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{{\bf Current Address} \\ 118 East Squire Drive \#8 \\ Rochester, NY 14623 \\ }

\address{{\bf Permanent Address} \\ 1405 Hornell LN\\Smyrna, GA 30082}
 
\begin{resume} 
 
\section{Objective} 
To obtain an intern or full-time position in the design and development of computing systems and software products. Available starting June 2010.

\section{Education} 
Rochester Institute of Technology, Rochester, NY ~~~~~May 2010\\
M.S. in Computer Science, Concentration in Distributed Systems ~~~~~GPA: 3.9 \\
\\
South China Normal University, GuangZhou, China ~~~~~July 2008\\
M.S. in Computer Science, Concentrations in Distributed Systems \\
\\
Hunan University, ChangSha, China  ~~~~~July 2000\\
B.S. in Computer Science

\section{Skills}
{\bf Programming:} C, C++, C\#, Java, VB, Delphi, Python, PHP, ASP.net, Javascript, UNIX shell scripting and others. \\
{\bf Database:} Oracle, Informix, MSSQL, MySQL.\\
{\bf Tools:} Latex, Microsoft Office, Eclipse and others.\\
{\bf Operating Systems:} Microsoft Windows XP/2000/2003, Apple OS X, Linux, SCO, AIX and other UNIX variants.\\
{\bf Concepts:} TCP/IP, Web Services, Distributed Computing, Algorithm.\\
{\bf Others:} Able to handle many projects simultaneously, and able to work effectively in a collaborative team environment.\\
%{\bf Programming Languages: } Java, C, C\#, ASP.net, Delphi, VB, HTML, Javascript, Shell script \\
%{\bf Operating Systems: } UNIX/Linux, Windows, Mac OS X\\
%{\bf Technique: } TCP/IP, Web Services, Parallel Computing, Algorithm\\

\section{Projects}
{\bf Master's Project}
Working on Parallel Java (PJ), an API and middleware for parallel programming in 100\% Java.

{\bf Research Project}
Participated in the Cyberaide Shell, an advanced but simple to use system shell facilitating the use of current and future cyberinfrastrucuture.

\section{Experience}

{\bf Software R\&D Intern }  Beijing Aoshi Inc., Beijing, China 2006-2007
\begin{itemize}
\item Designed and developed the online transaction platform for Guangzhou Social Insurance Bureau using J2EE.
\item Designed and developed the LED subsystem for the Second Asian Indoor Games using Java.
\item Designed and developed the Score subsystem for the Ninth GuangDong Games using Delphi. 
\item Participated in the development of IT Service Management Software, Project Management Software, Bug Management Software using ASP.net. 
\end{itemize}
%\\
%Lecturer Intern 2005-2006\\ 
%Give lectures on Web Services.\\ 
%Give lectures on Java Language.\\
{\bf Software Engineering } Giantstone IT Inc., Beijing, China 2002-2005
\begin{itemize}
\item Participated in the development of MinSheng Banking System using EC and Java. 
\item Participated in the development of Card SubSystem of Industrial and Commercial Bank of China using EC.
\end{itemize}

\section{Publications}

\begin{itemize}
\item Wang, L., A. J. Younge, T. R. Furlani, G. von Laszewski, J. Dayal, and X. He, "Towards Thermal Aware Workload Scheduling in a Data Center", 10th International Symposium on Pervasive Systems, Algorithms and Networks (I-SPAN 2009) , Kao-Hsiung, Taiwan, 12/2009, Accepted.
\item Laszewski, G., Wang L., Younge A. J., and He X.,  "Power-Aware Scheduling of Virtual Machines in DVFS-enabled Clusters",  IEEE Cluster 2009, New Orleans, Louisiana, IEEE, 08/2009.
\item Laszewski, G., Younge A., He X., Mahinthakumar K., and Wang L.,  "Experiment and Workflow Management Using Cyberaide Shell",  4th International Workshop on Workflow Systems in e-Science (WSES 09) in conjunction with 9th IEEE International Symposium on Cluster Computing and the Grid: IEEE, 2009.
\item Laszewski, G., Wang F., Younge A., He X., Guo Z., and Pierce M.,  "Cyberaide JavaScript: A JavaScript Commodity Grid Kit",  GCE08 at SC'08, Austin, TX, IEEE, Nov. 16, 2008.
\end{itemize}

\section{Honors}
Graduate Assistantship 2008-2009, Rochester Institute of Technology\\
Sun Certified Programmer for Java 2 platform, SE\\
Sun Certified Web Component Developer for Java 2 platform, EE

\section{References}
Available on request
\end{resume} 
\end{document} 



