% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.
  
\documentclass[12pt]{article}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{setspace}
%\usepackage[T1]{fontenc}

% Comment the following line to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
%\usepackage[sc,osf]{mathpazo}

% In practice, I use the following font packages instead of mathpazo.
% beramono provides a nice fixed-width font. xagaramon uses the
% (commercial) Adobe Garamond font.
%\usepackage[scaled=0.75]{beramono}
%\usepackage[osf]{xagaramon}

% Set your name here
\def\name{Xi He}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, econometrics, industrial organization,
    applied microeconomics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 10in},
  left=1.0in,
  top=1in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{2em}

% Make lists without bullets
%\renewenvironment{itemize}{
%  \begin{list}{}{
%    \setlength{\leftmargin}{1.5em}
%  }
%}{
%  \end{list}
%}

\begin{document}

\newcommand{\AUTHOR}{%
Xi He\\
%Rochester Institute of Technology\\
%~Bldg 74, Lomb Memorial Drive, Rochester, NY 14623-5608 \\
%~xi.he@mail.rit.edu%
}
\newcommand{\TITLE}{Personal Information Statement}

%\TABLEOFCONTENTS

\title{\TITLE}
\author{\AUTHOR}
%\maketitle
% Place name at left


% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}


.
%    \begin{itemize}
%    \item \textit{Minors:} Economics and Computer Science.
%    \item \textit{Honors:} \textit{Summa Cum Laude},
%      \href{http://www.pbk.org/}{Phi Beta Kappa}.
%    \item \textit{Advanced study:}
%      \href{http://www.stolaf.edu/depts/math-old/budapest/}{Budapest
%        Semesters in Mathematics}, Fall 2002.
%    \end{itemize}


\begin{center}
{\large {\em Personal Information Statement}}\\
~\\ 
{\small{\em Xi He }}
{\small{\em xxh2229@rit.edu}}
\end{center}
~\\
\begin{spacing}{1.5}
I am Xi He from China. I was enrolled in Computing and Information Sciences PhD program in RIT in 2008 and at that time everything seemed just fine since as a PhD student I was waived the tuition fee and got an assistantship which can cover all of my expenses. I studied hard and got a 4.0 GPA in my first year study. At the same time, I cooperated with my advisor and published several papers in conferences. However, my advisor, Dr. Laszewski left RIT in the past summer quarter for his personal reason, and no other faculty in my research field is available. As a result, it is very hard for me to continue my PhD studies without an academic advisor.

This quarter I decide to transfer to Computer Science Master Program and pursue my master degree in RIT. Since I am allowed to transfer some course credits to this program, I just need a few courses and a master thesis to get my master degree. My problem is that I can not apply for jobs like research assistants or teaching assistants. Although I never spent money on traveling or buying a car and I even share a two-bedroom apartment with two other friends, I am afraid that my savings are still not enough to pay for the expensive tuition fee and living expenses, and I also need to support my parents in China. 
 
I have talked to Dr. Bischof, the chair of the Computer Science Master Program, about my financial situation. Based on my good scores, the program might be able to provide some financial support to me. But up to now I am still waiting for the official decision.

I greatly appreciate your time and consideration. 

\end{spacing}

% Footer
%\begin{center}
%  \begin{footnotesize}
%    Last updated: \today \\
%    \href{\footerlink}{\texttt{\footerlink}}
%  \end{footnotesize}
%\end{center}
\end{document}