% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.
 
\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[T1]{fontenc}

% Comment the following line to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[sc,osf]{mathpazo}

% In practice, I use the following font packages instead of mathpazo.
% beramono provides a nice fixed-width font. xagaramon uses the
% (commercial) Adobe Garamond font.
%\usepackage[scaled=0.75]{beramono}
%\usepackage[osf]{xagaramon}

% Set your name here
\def\name{Xi He}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, econometrics, industrial organization,
    applied microeconomics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}[t]{0.5\textwidth}
  {Graduate Student}\\
  %\href{http://www.gccis.rit.edu/~gccisphd/phd/index.maml}{Second Year PhD Student} \\
  \href{http://www.rit.edu/}{Rochester Institute of Technology} \\
  %Bldg. 74, Room 1065\\
 102 Lomb Memorial Avenue\\
  Rochester, NY  14623  \\
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  Phone: (404) 518-3581 \\
  %Fax: (919) 684-8974 \\
  Email: \href{mailto:xi.he@mail.rit.edu}{\tt xi.he@mail.rit.edu} \\
  Skype: hexi111
  %Homepage: \href{http://cyberaide.org/members/he-xi}{\tt http://cyberaide.org/members/he-xi} \\
\end{minipage}

\section*{Education}

\begin{itemize}
  \item M.S. Computing Science, Rochester Institute of Technology,  2008-present.

  \item M.S. Computer Science, South China Normal University, 2005-2008.

  \item B.S. Computer Science, HuNan University, 1996-2000.
%    \begin{itemize}
%    \item \textit{Minors:} Economics and Computer Science.
%    \item \textit{Honors:} \textit{Summa Cum Laude},
%      \href{http://www.pbk.org/}{Phi Beta Kappa}.
%    \item \textit{Advanced study:}
%      \href{http://www.stolaf.edu/depts/math-old/budapest/}{Budapest
%        Semesters in Mathematics}, Fall 2002.
%    \end{itemize}

\end{itemize}

\section*{Research Interests}

Grid Computing,  Embedded Systems, Cloud Computing, Green Computing, Parallel Computing.

\section*{Research Activity}
\begin {itemize}
\item Participate in the research project {\em Parallel Java}, which is an API and middleware for parallel programming in 100\% Java.
\item Participate in the research project {\em Cyberaide JavaScript}, which is an easy-access JavaScript grid abstraction layer.
\item Participate in the research project {\em Cyberaide Shell}, an advanced but simple to use system shell facilitating the use of current and future cyberinfrastrucuture.
\item Participate in the research project {\em An Adaptive Cyberinfrastructure for 
Threat Management in Urban Water Distribution Systems}.
\item Collaborate with \href{http://www.ccr.buffalo.edu/display/WEB/Home} {Center for Computational Research} for the {\em Green Computing} project.
\end {itemize}


\section*{Publications}

\begin{itemize}
\item X. He, "Thermal Aware Task Scheduling With Artificial Neural Network", The First International Green Computing Conference, Chicago, IL, Aug. 15, 2010, Submitted.
\item Wang, L., A. J. Younge, T. R. Furlani, G. von Laszewski, J. Dayal, and X. He, "Towards Thermal Aware Workload Scheduling in a Data Center", 10th International Symposium on Pervasive Systems, Algorithms and Networks (I-SPAN 2009) , Kao-Hsiung, Taiwan, 12/2009, Accepted.
\item Laszewski, G., Wang L., Younge A. J., and He X.,  "Power-Aware Scheduling of Virtual Machines in DVFS-enabled Clusters",  IEEE Cluster 2009, New Orleans, Louisiana, IEEE, 08/2009.
\item Laszewski, G., Younge A., He X., Mahinthakumar K., and Wang L.,  "Experiment and Workflow Management Using Cyberaide Shell",  4th International Workshop on Workflow Systems in e-Science (WSES 09) in conjunction with 9th IEEE International Symposium on Cluster Computing and the Grid: IEEE, 2009.
\item Laszewski, G., Wang F., Younge A., He X., Guo Z., and Pierce M.,  "Cyberaide JavaScript: A JavaScript Commodity Grid Kit",  GCE08 at SC'08, Austin, TX, IEEE, Nov. 16, 2008.
\end{itemize}



\section*{Professional Experience}

Software R\&D Intern 2006-2007
\begin{itemize} 
\item Participate in the development of Embedded Systems for the Ninth GuangDong Games.
\item Design and develop the online transaction platform for Guangzhou Social Insurance Bureau.
\item Design and develop the LED subsystem for the Second Asian Indoor Games.
\item Design and develop the Score subsystem for the Ninth GuangDong Games.
\item Participate in the development of IT Service Management Software.
\item Participate in the development of Project Management Software.
\item Participate in the development of Bug Management Software.
\end{itemize} 
Teaching Intern 2005-2006
\begin{itemize}
\item Web Services.
\item Java Programming.
\end{itemize} 
Software Engineering 2002-2005
\begin{itemize}
\item Participate in the development of MinSheng Banking System.
\item Participate in the development of Card SubSystem of industrial and Commercial Bank of China.
\end{itemize} 

\section*{Technical Skills}
\begin {itemize}
\item Programming: C, C++, C\#, Java, VB, Delphi, Python, PHP, UNIX shell scripting and others.
\item Database: Oracle, Informix, MSSQL, MySQL.
\item Application: Latex, Microsoft Office, and other common productivity packages for Windows, OS X, Linux platforms.
\item Operating Systems: Microsoft Windows XP/2000/2003, Apple OS X, Linux, SCO, AIX and other UNIX variants.
\end {itemize}

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
